UKB Models

### 2023-09-29 ukb_mods.Rmd

#write data
write_csv(ukb_df, file="data/ukb_CN_data.csv")
```

@@

Seems like stepGAICAll handles combined sex.age term better than an interaction
Try adding TBV
```{r}
m3.tbv <- gamlss(formula = GMV ~ pb(age_days) + sex + fs_version + pb(sex.age) + pb(TBV),
                       sigma.formula = ~  pb(age_days) + sex,
                       nu.formula = ~ 1,
                       control = gamlss.control(n.cyc = 200), 
                       family = BCCG, data=ukb_df, trace = FALSE)
m4.tbv <- stepGAICAll.A(m3, scope=list(lower=~1, upper=~pb(age_days) + sex + fs_version + pb(sex.age) + pb(TBV)), k=2) #AIC
summary(m4.tbv)
```

>>>>

#write data
write_csv(ukb_df, file="data/ukb_CN_data.csv")

col_list <- colnames(ukb_df)
pheno_list <- col_list[grepl("^lh_|^rh_|^GMV$|^WMV$|^sGMV$|^Ventricles$", col_list)]
writeLines(pheno_list, con = "phenotype_list.txt")
```

@@

Seems like stepGAICAll handles combined sex.age term better than an interaction
Try adding TBV
```{r}
m3.tbv <- gamlss(formula = GMV ~ pb(age_days) + sex + fs_version + pb(sex.age) + pb(TBV),
                       sigma.formula = ~  pb(age_days) + sex,
                       nu.formula = ~ 1,
                       control = gamlss.control(n.cyc = 200), 
                       family = BCCG, data=ukb_df, trace = FALSE)
m4.tbv <- stepGAICAll.A(m3, scope=list(lower=~1, upper=~pb(age_days) + sex + fs_version + pb(sex.age) + pb(TBV)), k=2, glim.control(cyc=100)) #AIC
summary(m4.tbv)
```
